\section{Introduction}
Memory leak is a standard cause of errors in low-level programming languages
such as C and C++. Those languages provide manual memory management and require
explicit deallocation of structures. The category of errors can eventually
causes a system to run out of memory, and is difficult to identify.

We describe a \llvm~\cite{llvm} implementation on an analysis which
can detect a set of errors caused by the memory leak. The implementation is
based on a Dataflow algorithm using a worklist, proposed by Orlovich and 
Rugina~\cite{rugina}.

We analysis and detect the potential memory leak error
by checking whether a statement can cause a potential loss of reference to a 
heap cell. The definition of a leaked (error) cell is given~\cite{rugina} as: the 
program or the run-time system doesn't reclaim its memory when the lifetime 
has ended.

The analysis works as a backward Dataflow analysis. For each suspicious 
statement that can lead to a potential memory leak, the analysis assumes that 
it causes a loss of the last reference to the cell.
It then releases a detection probe to starts a backward 
Dataflow analysis from that programming point. If a contradiction is formed 
and the analysis reaches a $\bot$, the probe statement is proved to be safe. 
Otherwise, if the analysis reaches a $\top$, or it reaches the program entry, 
a warning of potential memory leak is released.

Section~\ref{s:algorithm} introduces the syntax, notations and algorithm
used within the report. Then, Section~\ref{s:implementation} discusses 
some implementation details, including the differences between the Rugina
~\cite{rugina} paper and our implementation; the discussion 
on branch and worklist management; and some improvements. 
Finally, the evaluation in Section~\ref{s:evaluation} is done through 
benchmarking. A set of 6 kinds
of microbenchmarks is used to show the correctness on different categories of
statements being analyzed. Then, two C programs from the GNU C Library source
code~\cite{glibc} are used to evaluate the performance on larger programs. No 
false positives are shown when analyzing the two GNU C programs.
